---
title: "Making Community Assignment Plot with Multiple Density"
date: "9/04/2019"
output: github_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gridExtra)

source("./commplot.R")

subject_comm <- read.csv('./sample_sub_sorted_community_mode.txt', header=F)
subject_sparse_mode <- read.table("./parcel_community.txt", header=T, sep="\t")
syslabel <- read.csv("./systemlabel.txt")

subject_sparse_mode[subject_sparse_mode==0] <- 1 # Liang name unassign to 0, but it should be named as 1 for coloring
colnames(subject_comm)[1:ncol(subject_comm)] <- seq(.1,10,.1) #  .1% to 10%

# Combine 0.1%-10% and sparsest & mode
c <- cbind(subject_sparse_mode, subject_comm)

g <- c %>% 
  select(-par_id, -par_vertex) %>%
  commplot(comm = ., 
           commlabel = syslabel, 
           ref_col='10', 
           col_order = c(rev(names(c)[3:7]), as.character(seq(.1,9.9,.1)), '10'), 
           comm_info=FALSE, 
           show_legend=TRUE)
```

# Overview

This Rmd shows how the function that makes the community plot is setup and gives an example of some tweaks that was made (and can be edited to change the plot). 

```{r, echo=FALSE, fig.width=10, fig.height=6}
print(g)
```


# Read in subject community matrix & add NodeID column

* This example has 100 columns of assignments, ordered from 0.1% to 10% edge density

```{r load subject}
c <- read.csv('./sample_sub_sorted_community_mode.txt', header=F)
csum <- read.table("./parcel_community.txt", header=T, sep="\t")

csum[csum==0] <- 1

# Rename Column name as Edge Density
colnames(c)[1:ncol(c)] <- seq(.1,10,.1) #  .1% to 10%

# Add NodeID column to matrix
c <- cbind(csum, c)
```

Show 9-10%
```{r}
head(c[as.character(seq(9.1,10,.1))])
```


## Sort the commnuity matrix 

* Adding a sorting column. Can be Power or the highest density (or whatever vector order you choose).
* This example uses Power

```{r sorting}
#### Edit to change reference order ####
# 10% edge density, can be replaced by Power/others
sorting_order <- order(c$power_label) 
##################################

sc <- c[sorting_order,]
sc$ReorderRef <- order(sc$power_label) # extract order of reordered reference and save it as a column
```

Sorted community matrix 9-10%
```{r}
head(sc[as.character(seq(9.1,10,.1))])
```


## Wide (matrix) to long data format (plotting purposes)

```{r mat_to_long}
# wide to long format
scc <- sc %>%
  gather("td", "CommID", -par_id, -par_vertex, -ReorderRef)

scc$td <- factor(scc$td, levels = c(rev(names(csum)[4:ncol(csum)-1]),
                                    as.character(seq(.1,10,.1)),
                                    'power_label')) # Order the Edge Density factor levels

```

## Make a new column of reassigned community labels

* Here the reassignment was done by assigning anything above `41` as `1`. 
* Other type of reassignemnts can be done where communities fewer than N nodes are assigned to `1`

```{r reassign}
scc$CommID_reassigned <- scc$CommID 
scc$CommID_reassigned[scc$CommID>41] <- 1 # unassigned
scc$CommID_reassigned <- factor(scc$CommID_reassigned)
```

Long format data frame with reassigned labels
```{r show_reassign}
head(scc)
```


## Setup the Color Palette

* This uses a systemlabel.txt file that already has information of how each community should be colored.

```{r}
syslabel <- read.csv("./systemlabel.txt")
head(syslabel)
```

* A color palette `syscolor` is created to be feed into ggplot. 
  + Note that the color for communities that don't exist in this subject is filtered out. 

```{r col_palette}
# Make color excluding those not in this subject
comm_in_sub <- is.element(syslabel$CommID, scc$CommID_reassigned)
syscolor <- as.character(syslabel$hex[comm_in_sub])
names(syscolor) <- as.character(syslabel$CommID[comm_in_sub])

head(syscolor)
```


## Basic Community plot sorted by Parcel ID or an Atlas (Power et al. 2011)

* Used `scale_x_discrete(limits=rev(levels(scc$td)))` to flip x axis to have higher density on the left

```{r basic_plot,  fig.width=20, fig.height=6}
g1 <- scc %>%
  ggplot(aes(x = td, y = par_id)) +
  geom_raster(aes(fill=CommID_reassigned)) +
  scale_y_reverse() +
  scale_x_discrete(limits=rev(levels(scc$td))) +
  xlab("Edge Density (%) / Label") +
  ylab("Parcel Index") +
  scale_fill_manual(values = syscolor) +
  ggtitle("Sorted by NodeID") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1, size=8))

g2 <- scc %>%
  ggplot(aes(x = td, y = ReorderRef)) +
  geom_raster(aes(fill=CommID_reassigned)) +
  scale_y_reverse() +
  scale_x_discrete(limits=rev(levels(scc$td))) +
  xlab("Edge Density (%) / Label") +
  ylab("Node orderd by Power") +
  scale_fill_manual(values = syscolor) +
  ggtitle("Sorted by 10% Edge Density") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1, size=8))

grid.arrange(g1, g2, ncol=2)
```



## Add number of unique communities on top

* 1. Count N community is at each density (before any reassignment)
* 2. Count N community with 5 or more nodes
* 3. Count N singletons (community with only 1 node)
* Position all of these above above the original plot using `geom_text()`

```{r add_num, fig.width=10, fig.height=5.5}
u_comm <- scc %>%
  group_by(td) %>%
  summarise(count=n_distinct(CommID))
u_comm$y <- -8 

u_comm_5p <- data.frame(td=levels(scc$td), 
                                 y=-33,
                                 count=sapply(X = levels(scc$td),
                                              FUN = function(x){sum(table(scc$CommID[scc$td==x]) >= 5)}))

u_comm_1 <- data.frame(td=levels(scc$td),
                             y=-53, 
                             count=sapply(X = levels(scc$td),
                                          FUN = function(x){sum(table(scc$CommID[scc$td==x]) == 1)}))

clabel <- data.frame(y=c(-8,-33,-53), 
                     td=11, 
                     label=c("N Comm","N Comm >=5","N Comm 1 node"))

g2 <- g2 + 
  # add community count info on top
  geom_text(data=u_comm, aes(x=td, y=y, label=count), angle = 90, size=3) +
  geom_text(data=u_comm_5p, aes(x=td, y=y, label=count), angle = 90, size=3) +
  geom_text(data=u_comm_1, aes(x=td, y=y, label=count), angle = 90, size=3) +
  geom_hline(yintercept = c(-23,-43), color="grey") + 
  geom_text(data=clabel, aes(y=y, label=label), x=0,
            hjust = 1,
            size = 3) +  
  coord_cartesian(# xlim = c(0.1, 10), # This focuses the x-axis on the range of interest
                  clip = 'off') +   # This keeps the labels from disappearing
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1, size=8),
        plot.margin = unit(c(1,1,1,3), "lines")) # This widens the left margin

print(g2)
```

## Show color legend

* Add short-name of label to make legend for color

```{r add_legend, warning=F, fig.width=14, fig.height=8}
g2 <- suppressMessages(g2 + scale_fill_manual(values = syscolor, 
                    name = "Community",
                    labels = as.character(syslabel$ShortName[comm_in_sub])) +
  theme(legend.position = "right"))

print(g2)
```
